A Realistic Guide to Making Data Available Alongside Code to Improve Reproducibility

### 2019-06-26 paper.Rmd
add bioconductor description, close #17

>>>>

Unlike CRAN, bioconductor, does not have a 5 megabyte limit for package size. They have a strict specification for how to organise genomic data in a package, so they can be used for data analysis out of the box. This is a robust solution, but only works for homogeneous data as found with bioinformatics. For example, data in their ExperimentData section (bioconductor.org/packages/3.9/data/experiment) can be used in a reliable way. However, such a strict standard would be impossible to enforce or scale on a repository as heterogeneous as CRAN.

However, these packages are still generally used for demonstration or testing purposes, over generating new knowledge for papers.
